---
title: "GEE Preparations"
author: "Marvin Ludwig"
date: '2022-03-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Aim

Lucas points were surveyed on different time days of the year.

```{r}
library(sf)
library(lubridate)
library(dplyr)
library(mapview)

mapviewOptions(fgb = FALSE)


lucas = st_read("data/raw/lucas_2018_checked_v1_2021-12-14.gpkg")

lucas_time = data.frame(date = lucas$survey_date)
lucas_time = lucas_time %>% group_by(date) %>% summarise(n = n())
lucas_time$date = lubridate::as_date(lucas_time$date)

plot(n ~ date, data = lucas_time)
```


For the development of satellite based models we need the matching imagery as close as possible to the survey date.

## GEE


Let's test the predictor acquisition with Google Earth Engine with a small sample.


```{r}
lucas_sample = lucas %>% filter(survey_date == "2018-05-03")
mapview(lucas_sample)
```


GEE expects a csv. So we have to reformat. This can be uploaded in the GEE Editor Assets.


```{r}
lucas_samples = lucas_sample %>% mutate(X = st_coordinates(lucas_sample)[,1],
                                        Y = st_coordinates(lucas_sample)[,2]) %>% 
    st_drop_geometry()

write.csv(lucas_samples, file = "data/gee/lucas_sample.csv", quote = TRUE, row.names = FALSE)
```

The following is a minimal example of a GEE script in JS:

```{js, eval = FALSE}
// Load sample points

var lucas = ee.FeatureCollection('users/Ludwigm6/lucas_sample');

// Load Sentinel 2 imagery
var sen = ee.ImageCollection("COPERNICUS/S2_SR")
              .filterDate('2018-05-03', '2018-05-15')
              .median();
              
              
              
// Sample Image at point locations
var sampledPoints = sen.sampleRegions({
  collection: lucas,
  scale: 10
});

// save to Google Drive
Export.table.toDrive(sampledPoints);

```


which results in the following extraction:


```{r}
lucas_gee = read.csv("data/gee/lucas_sample_gee.csv")
colnames(lucas_gee)
```

The used image collection (S2_SR) also includes the SCL band which we can use to filter the training data without fancy GEE scripting.






